Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-04 PAPER.tex
added new FRF plot
consistent variable notation in signal loss section

@@

\begin{equation}
\label{eq:Pin}
P_{\rm in,\alpha} = \textbf{M}_{ii}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
\end{equation}

@@

\begin{eqnarray}
\label{eq:sigloss}
P_{\rm out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
&=& \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
^{\alpha}\textbf{R}_{x}\textbf{x},
\end{eqnarray}
where, for illustrative purposes, all $\textbf{M}$'s are diagonal normalizations. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
$\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
data plus injection, and $P_{\rm out}$ is the difference between $\hat{\textbf{p}}_{r}$ and $\hat{\textbf{p}}_{x}$.

@@

In a limit with no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
\begin{equation}
\x \equiv \f + \s,
\end{equation}
where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal. In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat$. This can be parametrized as
\begin{equation}
\label{eq:LinearPspecSum}
\langle \phat \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
\end{equation}
where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the result is an approximation.

Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate. Although such an estimate leaves an additive bias from foregrounds that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias. The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
\begin{equation}
\label{eq:Deriv1}
\hat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
\end{equation}
However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether! Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $\p^*_{\rm eor}$), computing instead
\begin{equation}
\label{eq:Deriv2}
\hat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{\p^*_{\rm eor}},
\end{equation}
which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}. Essentially, one is computing the slope of $\langle \phat \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives). Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$. In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.

@@

One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
estimate, decreasing the value of $P_{\rm out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:

\begin{eqnarray}
\label{eq:crossterm}
P_{\rm out,\alpha} &=& \textbf{M}_{rr}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
\textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
&=& \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
&-& \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}

@@

\begin{eqnarray}
\label{eq:pout_expand}
P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=&  \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
 \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
 &+&  \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
\end{eqnarray}

@@

We now explain why the spurious correlations between $\textbf{e}$ and $\textbf{x}$ contain negative power.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
can become anti-correlated on average. 
This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. 
Intuitively, we can see this by expanding the covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
$|\textbf{x}|\ll|\textbf{e}|$ regime:

\begin{eqnarray}
\textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle \\
&=& \langle \textbf{xx}^{\dagger} \rangle + \langle \textbf{xe}^{\dagger} \rangle + \langle \textbf{ex}^{\dagger} \rangle + \langle 
\textbf{ee}^{\dagger} \rangle,
\end{eqnarray}

@@

\begin{eqnarray}
P_{\rm in,\alpha} &=&  \textbf{M}_{ii}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
P_{\rm out,\alpha} &=&  \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
&&\phantom{=====} -  \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
\end{eqnarray}

@@

The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections. Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat)$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat$, which is given by
\begin{equation}
\label{eq:Bayes}
p( \p_{\rm eor} | \phat) \propto \mathcal{L} (  \phat | \p_{\rm eor})  p( \p_{\rm eor}),
\end{equation}
where $p( \p_{\rm eor})$ is the prior on $\p_{\rm eor}$ and $\mathcal{L} $ is the likelihood function. Since the likelihood is defined as the distribution of the measured result $ \phat$ given the theoretical power spectrum $\p_{\rm eor}$, we may construct this function simply by fixing $\p_{\rm eor}$, and simulating our analysis pipeline for many realizations of the injected EoR signal consistent with this power spectrum. The resulting distribution can be normalized, and the whole process can then be repeated for a different value of $\p_{\rm eor}$.

In our code, we simulate $20$ realizations of $\p_{\rm eor}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$. We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs. $P_{\rm out}$ grid. 
%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators. The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}. Bayes' rule then simply instructs us to fix $\phat$ at our measured value $\phat_{x}$, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p( \p_{\rm eor})$. The final result can then be normalized to give $p( \p_{\rm eor} | \phat)$. If $\phat$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat$, before performing the final summation and normalization. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\hat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\hat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.

>>>>

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
	\caption{.}
	\label{fig:toy_sigloss16}
\end{figure}

@@

\begin{equation}
\label{eq:Pin}
P_{\rm in,\alpha} \equiv M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
\end{equation}

@@

\begin{eqnarray}
\label{eq:sigloss}
P_{\rm out,\alpha} &\equiv& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
&=& M_{\alpha}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
^{\alpha}\textbf{R}_{x}\textbf{x},
\end{eqnarray}
\cc{fix!}where, for illustrative purposes, all $M$'s are diagonal normalizations. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
$\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
data plus injection, and $P_{\rm out}$ is the difference between $\hat{\textbf{p}}_{r}$ and $\hat{\textbf{p}}_{x}$.

@@

In a limit with no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
\begin{equation}
\x \equiv \f + \s,
\end{equation}
where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal. In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat_{x}$. This can be parametrized as
\begin{equation}
\label{eq:LinearPspecSum}
\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
\end{equation}
where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the result is an approximation.

Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate. Although such an estimate leaves an additive bias from foregrounds that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias. The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
\begin{equation}
\label{eq:Deriv1}
\hat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
\end{equation}
However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether! Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $P_{in}$), computing instead
\begin{equation}
\label{eq:Deriv2}
\hat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
\end{equation}
which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}. Essentially, one is computing the slope of $\langle \phat_{x} \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives). Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$. In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.

@@

One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
$P_{\rm out,\alpha} = M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
estimate, decreasing the value of $P_{\rm out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:

\begin{eqnarray}
\label{eq:crossterm}
P_{\rm out,\alpha} &=& M_{\alpha}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
&=& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
&-& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}

@@

\begin{eqnarray}
\label{eq:pout_expand}
P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
 M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
 &+&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
\end{eqnarray}

@@

We now explain why the spurious correlations between $\textbf{e}$ and $\textbf{x}$ contain negative power.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
can become anti-correlated on average. 
This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. 
Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
$|\textbf{x}|\ll|\textbf{e}|$ regime:

\begin{eqnarray}
\textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \\
&=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
\textbf{ee}^{\dagger} \rangle_{t},
\end{eqnarray}

@@

\begin{eqnarray}
P_{\rm in,\alpha} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
&&\phantom{=====} 
-  M_{\alpha}\textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
\end{eqnarray}

@@

The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections. Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$. Since Equation \eqref{eq:Deriv2} is a good approximation of Equation \eqref{eq:Deriv1}, which we argued for in the previous section, we can write $\p_{\rm eor}$ as $P_{in}$, and hence the probability distribution is given by
\begin{equation}
\label{eq:Bayes}
p(P_{in} | \phat_{x}) \propto \mathcal{L} (  \phat_{x} | P_{in})  p(P_{in}),
\end{equation}
where $p(P_{in})$ is the prior on $P_{in}$ and $\mathcal{L} $ is the likelihood function. Since the likelihood is defined as the distribution of the measured result $ \phat_{x}$ given the theoretical power spectrum $P_{in}$, we may construct this function simply by fixing $P_{in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal consistent with this power spectrum. The resulting distribution can be normalized, and the whole process can then be repeated for a different value of $P_{in}$.

In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$. We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs. $P_{\rm out}$ grid. 
%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators. The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}. Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$. The final result can then be normalized to give $p(P_{in} | \phat_{x})$. If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\hat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\hat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
